---
title: "Assignment"
author: "Ankit Pandey - 437949"
date: today
output: html_document
---

```{r}
load("../Data/season_2.RData")
season_data <- read.csv("C:\\Users\\Ankit\\OneDrive\\Documents\\ReproducibleR\\RRcourse2023\\Data\\season_2.csv")
most_viewed <- season_data[which.max(season_data$viewers), ]

# Extract the title of the most viewed episode
most_viewed_title <- most_viewed$title
```

# Game of Thrones - Season 2 summary in numbers

### __(*Warning:* spoilers ahead)__

***

### Overview

(From the [Wikipedia](https://en.wikipedia.org/wiki/Game_of_Thrones#Premise)) Game of Thrones is an American fantasy drama television series created by David Benioff and D. B. Weiss for HBO. It is an adaptation of A Song of Ice and Fire, a series of fantasy novels by George R. R. Martin, the first of which is A Game of Thrones.

Set on the fictional continents of Westeros and Essos, Game of Thrones has a large ensemble cast and follows several story arcs throughout the course of the show. A major arc concerns the Iron Throne of the Seven Kingdoms of Westeros through a web of political conflicts among the noble families either vying to claim the throne or fighting for independence from it. Another focuses on the last descendant of the realm's deposed ruling dynasty, who has been exiled to Essos and is plotting a return to the throne. A third story arc follows the Night's Watch, a military order defending the realm against threats from the North.

***

### Season 2 summary

Season 2 of Game of Thrones consisted of `r nrow(season_data)` episodes that aired between `r min(season_data$premiere_date)` and `r max(season_data$premiere_date)` on HBO. The show gathered an average of `r mean(season_data$viewers)` first-day TV viewers in the US, with the number growing from `r min(season_data$viewers)` to `r max(season_data$viewers)` million by the end of the season.

The most popular episode of the season was `r most_viewed$title`, in which:
> "`r most_viewed$description`"


> "The episode concludes many storylines featured throughout the second season, such as Tyrion Lannister's position as Hand of the King, Stannis Baratheon's impending invasion, and Sansa Stark's betrothal to Joffrey Baratheon. In the episode, citizens of King's Landing deal with the aftermath of Stannis's failed attack on the city, with Tywin Lannister being named Hand of the King in Tyrion's stead; Sansa's engagement to Joffrey is annulled, and Margaery Tyrell is betrothed in her place; and Stannis broods in defeat at Dragonstone. Other plotlines include Brienne of Tarth escorting Jaime Lannister south, Jon Snow earning the trust of the Free Folk, and Daenerys Targaryen reuniting with her dragons in the House of the Undying. The episode's title is a code phrase spoken by Jaqen H'ghar to Arya Stark, but its meaning, "all men must die", is not explained until the next season.
Valar Morghulis received positive reviews from critics and audiences, and achieved a viewership of 4.20 million during its initial airing in the United States, setting a new record for the series. At the 64th Primetime Creative Arts Emmy Awards, the episode won the award for Outstanding Special Visual Effects and was nominated for Outstanding Prosthetic Makeup."

***

You can see how the viewership of the episodes changed in Figure 1.

```{r}
#| label = "viewers_plot"
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

***

Finally, the episodes with the above-average viewership were:

| No. in season | Title  | Directed by  |
|:------        |:-----: |:------:      |
| 5             | "The Night Lands"  | Alan Taylor      |
| 8             | "The Ghost of Harrenhal" | David Petrarca      |
| 9             | "Blackwater" | Alan Taylor      |
| 10            | "Valar Morghulis" | Alan Taylor      |
