---
title: "Meta-analysis in R"
author: "Ankit Pandey - 437949"
date: 23-07-2023
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
#setwd("")
```

```{r}
install.packages("meta")
```

## Metaanalysis

*a statistical analysis that combines the results of multiple scientific studies.* ([Wikipedia](https://en.wikipedia.org/wiki/Meta-analysis))

Very important in e.g. medicine (where it's relatively easy to use).

Can serve different goals:

1) Finding the "true" size of the relationship based on multiple studies.
2) Finding the average effect size based on multiple studies.
3) Finding what affects the relationship:
  - study-related (e.g. author effects, journal effects, method effects, variable selection, etc.)
  - context-related (e.g. changes over time, sample characteristics, country, etc.)
4) Uncovering publication biases (e.g. a meta-analysis of several studies with statistically significant results may conclude that there is not enough evidence)

```{r}
library(readxl)
data <- read_excel("C:\\Users\\Ankit\\OneDrive\\Documents\\ReproducibleR\\RRcourse2023\\13. Metaanalysis\\metaanalysis_data.xlsx")

```
## Case 1: Fixed Effects

```{r}
# Perform meta-analysis with fixed effects
fixed_effects <- meta::metagen(TE = Mean_boys_play_male,
                               seTE = SD_boys_play_male,
                               data = data,
                               studlab = paste(Study),
                               comb.fixed = TRUE,
                               comb.random = FALSE)

fixed_effects

```

## Case 2: Combining both Fixed and Random Effects

```{r}
# Perform meta-analysis with both fixed and random effects
mixed_effects <- meta::metacont(n.e = N_boys,
                                mean.e = Mean_boys_play_male,
                                sd.e = SD_boys_play_male,
                                n.c = N_boys,
                                mean.c = Mean_girls_play_male,
                                sd.c = SD_girls_play_male,
                                data = data,
                                studlab = paste(Study),
                                comb.fixed = TRUE,
                                comb.random = TRUE)

mixed_effects

```

## Case 3: Random Effect

```{r}
# Perform meta-analysis with random effect
random_effect <- meta::metagen(TE = Mean_boys_play_male,
                               seTE = SD_boys_play_male,
                               data = data,
                               studlab = paste(Study),
                               comb.fixed = FALSE,
                               comb.random = TRUE)

random_effect


```


```{r}
# Plot forest plot for fixed effects meta-analysis
fixed_effects %>% forest(sortvar = Mean_boys_play_male)

```



```{r}
# Perform meta-regression to explore effects of `Female authors` and `Male authors`
fixed_effects %>% metareg(~ `Female authors` + `Male authors`)

  
```  


## Creating Funnel Plot


```{r}
# Plot funnel plot for random effects meta-analysis
random_effect %>% funnel()

```

The above plot shows asymmetry or clustering of data points, it might indicate the presence of publication bias or heterogeneity.


```{r}
# Customize the funnel plot with contour levels and colors
contour_levels <- c(0.70, 0.75, 0.75)
contour_colors <- c("green", "red", "yellow")
funnel(random_effect, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)

```

